---
title: "HW9-TA"
output: md_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)
```


```{r, include=FALSE,echo=FALSE}
library(tidyverse)
library(MASS)
```

# Question 1. 
The Zoology department of The University of Adelaide was curious to see if Native snails and Exotic snails had the same ability to survive in different conditions. The two different species of snail were exposed to different relative humidities and temperatures for 1, 2, 3, or 4 weeks. The snail data is included in the package `MASS`. 

## A. 
 Plot a boxplot for each relative humitidy (one new plot for 60%, 65.8%, 70.5%, and 75.8% relative humidity). The x axis of the boxplot should be Temperature, the y axis should the the number of deaths, and the boxplots should be filled with the species type. 
```{r boxplot}
ggplot(snails, aes(x = as.factor(Temp), y = Deaths, fill = Species)) +
  geom_boxplot() +
  xlab("Temperature") +
  ggsci::scale_fill_locuszoom() +
  facet_wrap("Rel.Hum") +
  theme_bw()
```

## B. 
Use the appropriate statistical test to investigate whether Species A survives better than Species B in 60% Relative Humidity regardless of temperature. If you take temperature into account, does your conclusion change? 

Please report your answer by filling in the blanks below. 

* Null Hypothesis: There is no relationship between Species and Number of Deaths. 

* Test used and reason: We use Chi-squared because we are interested in the relationship between two categorical variables (Species and Death) and we want to see if they are independent. 

* P-value: 
```{r}
sixty_rel <- snails %>% 
  filter(Rel.Hum == 60)

# lets make a contingency table to clarify what we want
# at each condition there are 20 snails


print(cont <- sixty_rel %>% 
  group_by(Species) %>% 
  mutate(total_number_snails = sum(N)) %>% 
  mutate(total_number_deaths = sum(Deaths)) %>% 
  mutate(total_number_live_snails = total_number_snails - total_number_deaths) %>% 
  dplyr::select(Species, total_number_live_snails, total_number_deaths) %>% 
  distinct() %>% 
  column_to_rownames("Species"))


chisq.test(cont)
```


* Reject null? (Y/N) and why: Yes, because it is unlikely that Species and Death are independent (Pvalue 4.743e-06)

## Alternative B. 

* Null Hypothesis: There is no difference between the number of deaths in Species A and the number of deaths in Species B. 

* Test used and reason: We use a T-test because we are comparing the mean number of deaths. 

* P-value: 
```{r}
t.test(snails$Deaths ~ snails$Species)
```


* Reject null? (Y/N) and why: Yes, because it is unlikely that the number of deaths are the same between each species. (Pvalue 0.002432)


# Question 2. 
Now we will use the thyroid data. We want to know whether patients treated with different doses of the drug sorafenib respond differently. Split the patients into high treatment and low treatment at your discretion. Keep in mind that a more even split in the number of patients in each group is better. 
```{r, echo = FALSE, include = FALSE}
load("../../../Downloads/thyroid.RData")
```

```{r}
thyroid <- thyroid %>% 
  mutate(patient_split = ifelse(avgdose > 600, "High", "Low")) %>% 
  filter(!is.na(patient_split))
```

## A. 
Plot a boxplot of tumor response in the two patient groups. The x axis should be patient groups, the y axis should be tumor response.
```{r}
ggplot(thyroid, aes(x = patient_split, y = bestresp, fill = patient_split)) +
  geom_boxplot() +
  theme_bw() + 
  ggsci::scale_fill_futurama()
```


## B. 
Use the appropriate statistical test to investigate whether tumor response is different between the two groups.

Please report your answer by filling in the blanks below. 

* Null Hypothesis: The mean best response between the two patient groups are the same. 

* Test used and reason: We use a T-test because we are comparing the means of bestresp. 

* P-value:
```{r}
t.test(thyroid$bestresp ~ thyroid$patient_split)
```

* Reject null? (Y/N) and why: At the arbitrarily chosen significance level of 0.05, we fail to reject the null hypothesis because P > 0.05. However, as Dr. Troxel mentioned in class, we are moving away from using an arbitrary significance level and moving towards embracing uncertainty, so this question was not great. Sorry!


# Question 3. 

## A
You want to design a new study comparing a new chemotherapy to radiation for breast cancer. The outcome you are measuring is the reduction of tumor size. You want a sample size of n=100/treatment arm. You expect that the average difference in tumor size reduction in the chemotherapy group vs radiation group will be 2, and standard deviation will be equal to 5. What power will this yield?
```{r}
power.t.test(n=100, delta=2, sd=5, power=NULL)
```


## B
If we wanted 90% power, what sample size would we need? (Keeping all other parameters the same)
```{r}
power.t.test(n=NULL, delta=2, sd=5, power=0.90)
```


## C
How would the power be affected by decreasing the standard deviation? 

Power decreases with increasing standard deviation. 

## D
How would the power be affected by increasing the effect size?

The power increases by increasing the effect size. 


# Question 4. 
Now we will use the Mauna Loa C02 concentrations dataset. We will predict the response of the Temperature based on Wind.

A reminder: 

### Residual 
Deviation of the observed value to the estimated value. 

### Here are some assumptions that linear regression makes: 
* The residuals should be close to zero.
* There should be equal variance around the regression line (homoscedasticity).
* Residuals should be normally distributed.
* Independent variables and residuals should not be correlated.

```{r}
data(airquality)
```


This is the data we will fit a linear model to. 
```{r, echo = FALSE}
ggplot(data = airquality) +
  geom_point(aes(x=Wind, y=Temp)) +
  theme_bw()
```

## A.
Create and fit a linear model to predict Temperature from Wind.

```{r}
linear_regression <- lm(Temp ~ Wind, data = airquality)
```


## B.
Vizualize how your model performed on the data by plotting the regression line on top of the data points. 
```{r}
linear_predict <- predict(linear_regression)
plot_lin_pred <- data.frame(Temp_pred = linear_predict, Temp = airquality$Temp, Wind = airquality$Wind)

# Extract coefficients from the model, plot the regression line on the predicted values, plot the original test values
linear_regression$finalModel$coefficients

ggplot(data = plot_lin_pred)+
  geom_point(aes(x=Wind, y = Temp_pred, col =  "Predicted")) + 
  ggtitle("Linear Regression model on Test Set") +
  geom_abline(aes(intercept = 90.493474, slope = -1.27743, col="Regression Line")) +
  geom_point(aes(x = Wind, y = Temp, col = "Observed values")) +
  geom_segment(aes(x = Wind, xend = Wind, y = Temp,yend = Temp_pred)) +
  theme_bw() +
  ggsci::scale_color_aaas()

```


## C. 
Look at the residuals. Are they close to zero? 
```{r}
summary(linear_regression)
```
The median residual is 1.709 which is not too bad. But if you look at the 1st and 3rd Quartile, as well as the max and min residuals, they are quite large given that Temp has a range of ~40. 

## D. 
Plot predicted temperature vs observed temperature. A strong model should show a strong correlation.
```{r}

ggplot(data = plot_lin_pred) +
  geom_point(aes(x=Temp, y = Temp_pred)) +
  ggtitle("True Temp Value vs Predicted Temp Value Linear Regression") +
  theme_bw()

```


## E. 
Plot Wind vs predicted Temperature, and on the same plot, add Wind vs measured Temperature, and the regression line.
```{r}
# Extract coefficients from the model
# plot the regression line on the predicted values
# plot the original test values

ggplot(data = plot_lin_pred) +
  geom_point(aes(Wind, Temp_pred), color = "red") +
  geom_point(aes(Wind, Temp), color = "dark blue") +
  geom_abline(aes(intercept = 90.493474, slope = -1.27743, col="Regression Line"))  +
  theme_bw()

  
```

## F. 
Residuals should be normally distributed. Plot the density of the residuals. Are they normally distributed? (help(residuals))
```{r}
residuals_lin <- residuals(linear_regression)
residvpredict <- data.frame(residual = residuals_lin, Wind = airquality$Wind)

ggplot(data=residvpredict) +
  geom_density(aes(residual)) +
  theme_bw()
```

## G.
Independent variables and residuals should not be correlated. Calculate the correlation between the Wind and the residuals. 
```{r}
cor.test(residvpredict$Wind, residvpredict$residual)
```

