---
title: "HW9-TA"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)
```


```{r, include=FALSE,echo=FALSE}
library(tidyverse)
library(MASS)
```

# Question 1. 
The Zoology department of The University of Adelaide was curious to see if Native snails and Exotic snails had the ability to survive in different conditions. The two different species of snail were exposed to different relative humidities and temperatures for 1, 2, 3, or 4 weeks. The snail data included in the package `MASS`. 

## A. 
We want to know whether Species A or Species B survives better in each of the conditions and each of the exposure times. Plot a boxplot for each relative humitidy (one new plot for 60%, 65.8%, 70.5%, and 75.8% relative humidity). The x axis of the boxplot should be Temperature, the y axis should the the number of deaths, and the boxplots should be filled with the species type. 
```{r boxplot, echo = FALSE}
ggplot(snails, aes(x = as.factor(Temp), y = Deaths, fill = Species)) +
  geom_boxplot() +
  xlab("Temperature") +
  ggsci::scale_fill_locuszoom() +
  facet_wrap("Rel.Hum") +
  theme_bw()
```

## B. 
Use the appropriate statistical test to investigate whether Species A survives bettern than Species B in 60% Relative Humidity regardless of temperature. If you take temperature into account, does your conclusion change? 

Please report your answer by filling in the blanks below. 

* Null Hypothesis: 

* Test used and reason:

* P-value:

* Reject null? (Y/N) and why:


# Question 2. 
Now we will use the thyroid data. We want to know whether patients treated with different doses of the drug sorafenib respond differently. Split the patients into high treatment and low treatment at your discretion. Keep in mind that a more even split in the number of patients in each group is better. 

## A. 
Plot a boxplot of tumor response in the two patient groups. The x axis should be patient groups, the y axis should be tumor response.


## B. 
Use the appropriate statistical test to investigate whether tumor response is different between the two groups.

Please report your answer by filling in the blanks below. 

* Null Hypothesis: 

* Test used and reason:

* P-value:

* Reject null? (Y/N) and why:


# Question 3. 

## A. 
What is the probability that at least two pairs of people (4 people are involved here. 2 people with one birthday, and another 2 people with another birthday) in a room of 20 share the same birthday. Please report your work. 

## B. 
What is the number of people that need to be present in a room in order for there to be a 50% chance that two people share the same birthday? Please report your work.




